---
title: "Your Personality Report"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-dependencies, include = F}
library(tidyverse)
library(plotly)
library(truncnorm)
```

```{r functions, include = F}
norm_dataset <- function(data, person, value){
  
  #creating hexaco norming data
  hexaco_norm <- data.frame(matrix(ncol = 0, nrow = 1126))

  set.seed(1998)

  hexaco_norm$hh <- rtruncnorm(1126, 1, 5, 3.23, .66)
  hexaco_norm$em <- rtruncnorm(1126, 1, 5, 3.36, .7)
  hexaco_norm$ex <- rtruncnorm(1126, 1, 5, 3.51, .62)
  hexaco_norm$ag <- rtruncnorm(1126, 1, 5, 3.10, .63)
  hexaco_norm$cn <- rtruncnorm(1126, 1, 5, 3.47, .61)
  hexaco_norm$op <- rtruncnorm(1126, 1, 5, 3.49, .67)

  #select person
  data <- data %>%
    filter(person == value)

  #get HEXACO scores
  hexaco_norm$op_score <- rep(data$openness, times = 1126)
  hexaco_norm$ag_score <- rep(data$agreeableness, times = 1126)
  hexaco_norm$ex_score <- rep(data$extraversion, times = 1126)
  hexaco_norm$cn_score <- rep(data$conscientiousness, times = 1126)
  hexaco_norm$hh_score <- rep(data$honestyhumility, times = 1126)
  hexaco_norm$em_score <- rep(data$emotionality, times = 1126)

  #get scores as percentiles
  hexaco_norm$op_qscore <- ecdf(hexaco_norm$op)(hexaco_norm$op_score)
  hexaco_norm$ag_qscore <- ecdf(hexaco_norm$ag)(hexaco_norm$ag_score)
  hexaco_norm$ex_qscore <- ecdf(hexaco_norm$ex)(hexaco_norm$ex_score)
  hexaco_norm$cn_qscore <- ecdf(hexaco_norm$cn)(hexaco_norm$cn_score)
  hexaco_norm$hh_qscore <- ecdf(hexaco_norm$hh)(hexaco_norm$hh_score)
  hexaco_norm$em_qscore <- ecdf(hexaco_norm$em)(hexaco_norm$em_score)

  hexaco_norm <- hexaco_norm %>%
    mutate(op_qscore = round(op_qscore*100),
           ag_qscore = round(ag_qscore*100),
           ex_qscore = round(ex_qscore*100),
           cn_qscore = round(cn_qscore*100),
           hh_qscore = round(hh_qscore*100),
           em_qscore = round(em_qscore*100))
  
  write.csv(hexaco_norm, file = "data/hexaco_norm.csv")
}
```

```{r generate data, include = F}
### INSTRUCTIONS
 ## insert the name of your dataset csv below, and give the dataset a name.

real_data <- read.csv("data/hexaco scores.csv")

 ## complete the function below such that 
  # data = the dataset you want to extract values from
  # person = the column that represents each person in your data (e.g., participant IDs)
    # for this to work, this argument should be in the form "data$column"
  # value = the the participant ID value corresponding to the particular person you want to get trait scores for

norm_dataset(real_data, real_data$ID, 34)

hexaco_norm <- read.csv("data/hexaco_norm.csv")

### If this works, you should have a dataset named hexaco_norm. Now, knit this entire document to create a personalized hexaco score report.
```

Your score on agreeableness shows that you are in the `r unique(hexaco_norm$ag_qscore)`th percentile for agreeableness. This means that you scored higher than `r unique(hexaco_norm$ag_qscore)`% of people on the dimension of agreeableness.

```{r ag-plot, echo=FALSE, warning=FALSE}
agplot <- ggplot(hexaco_norm, aes(x = ag))+
    geom_density(color = "steelblue4", fill = "steelblue1", linewidth = 0.9, bw = 0.3, alpha = 0.7)+
    geom_segment(aes(x = quantile(ag, probs = 0.5), y = 0, xend = quantile(ag, probs = 0.5), yend = 0.58, text = "Average"), color = "steelblue4", linetype = "dashed", linewidth = 0.4, alpha = 0.5)+
    geom_segment(aes(x = quantile(ag, probs = 0.01), y = 0.65, xend = quantile(ag, probs = 0.99), yend = 0.65), linewidth = 1, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.99), y = 0.65, text = "99th percentile"), size = 1.5, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.01), y = 0.65, text = "1st percentile"), size = 1.5, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.95), y = 0.65, text = "95th percentile"), size = 2, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.05), y = 0.65, text = "5th percentile"), size = 2, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.80), y = 0.65, text = "80th percentile"), size = 2.5, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.20), y = 0.65, text = "20th percentile"), size = 2.5, color = "steelblue3")+
    geom_point(aes(x = quantile(ag, probs = 0.5), y = 0.65, text = "Average"), size = 4, color = "steelblue3")+
    geom_segment(aes(x = ag_score, y = 0, xend = ag_score, yend = 0.65), color = "black", linewidth = 1)+
    geom_point(aes(x = ag_score, y = 0.65, text = ag_qscore), color = "black", size = 4.5)+
    geom_text(aes(x = ag_score, y = 0.68, label = "Your Score"))+
    theme_void()+
    scale_y_continuous(
      limits = c(0, 0.75),
      expand = c(0, 0))+
    labs(title = "Agreeableness")+
  theme(plot.title = element_text(hjust = 0.5))
  
ggplotly(agplot, tooltip = "text")
```

# Extraversion

Your score on extraversion shows that you are in the `r unique(hexaco_norm$ex_qscore)`th percentile for extraversion. This means that you scored higher than `r unique(hexaco_norm$ex_qscore)`% of people on the dimension of extraversion.

```{r extra-plot, echo = F, warning = F}
explot <- ggplot(hexaco_norm, aes(x = ex))+
    geom_density(color = "forestgreen", fill = "palegreen1", linewidth = 0.9, bw = 0.3, alpha = 0.7)+
    geom_segment(aes(x = quantile(ex, probs = 0.5), y = 0, xend = quantile(ex, probs = 0.5), yend = 0.58, text = "Average"), color = "forestgreen", linetype = "dashed", linewidth = 0.4, alpha = 0.5)+
    geom_segment(aes(x = quantile(ex, probs = 0.01), y = 0.65, xend = quantile(ex, probs = 0.99), yend = 0.65), linewidth = 1, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.99), y = 0.65, text = "99th percentile"), size = 1.5, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.01), y = 0.65, text = "1st percentile"), size = 1.5, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.95), y = 0.65, text = "95th percentile"), size = 2, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.05), y = 0.65, text = "5th percentile"), size = 2, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.80), y = 0.65, text = "80th percentile"), size = 2.5, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.20), y = 0.65, text = "20th percentile"), size = 2.5, color = "palegreen3")+
    geom_point(aes(x = quantile(ex, probs = 0.5), y = 0.65, text = "Average"), size = 4, color = "palegreen3")+
    geom_segment(aes(x = ex_score, y = 0, xend = ex_score, yend = 0.65), color = "black", linewidth = 1)+
    geom_point(aes(x = ex_score, y = 0.65, text = ex_qscore), color = "black", size = 4.5)+
    geom_text(aes(x = ex_score, y = 0.68, label = "Your Score"))+
    theme_void()+
    scale_y_continuous(
      limits = c(0, 0.75),
      expand = c(0, 0))+
    labs(title = "Extraversion")+
  theme(plot.title = element_text(hjust = 0.5))
  
  
ggplotly(explot, tooltip = "text")
```

# Honesty-Humility

Your score on honesty-humility shows that you are in the `r unique(hexaco_norm$hh_qscore)`th percentile for honesty-humility. This means that you scored higher than `r unique(hexaco_norm$hh_qscore)`% of people on the dimension of honesty-humility.

```{r hh-plot, echo = F, warning = F}
hhplot <- ggplot(hexaco_norm, aes(x = hh))+
    geom_density(color = "goldenrod4", fill = "gold1", linewidth = 0.9, bw = 0.3, alpha = 0.7)+
    geom_segment(aes(x = quantile(hh, probs = 0.5), y = 0, xend = quantile(hh, probs = 0.5), yend = 0.54, text = "Average"), color = "goldenrod4", linetype = "dashed", linewidth = 0.4, alpha = 0.5)+
    geom_segment(aes(x = quantile(hh, probs = 0.01), y = 0.6, xend = quantile(hh, probs = 0.99), yend = 0.6), linewidth = 1, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.99), y = 0.6, text = "99th percentile"), size = 1.5, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.01), y = 0.6, text = "1st percentile"), size = 1.5, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.95), y = 0.6, text = "95th percentile"), size = 2, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.05), y = 0.6, text = "5th percentile"), size = 2, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.80), y = 0.6, text = "80th percentile"), size = 2.5, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.20), y = 0.6, text = "20th percentile"), size = 2.5, color = "goldenrod3")+
    geom_point(aes(x = quantile(hh, probs = 0.5), y = 0.6, text = "Average"), size = 4, color = "goldenrod3")+
    geom_segment(aes(x = hh_score, y = 0, xend = hh_score, yend = 0.6), color = "black", linewidth = 1)+
    geom_point(aes(x = hh_score, y = 0.6, text = hh_qscore), color = "black", size = 4.5)+
    geom_text(aes(x = hh_score, y = 0.63, label = "Your Score"))+
    theme_void()+
    scale_y_continuous(
      limits = c(0, 0.7),
      expand = c(0, 0))+
    labs(title = "Honesty-Humility")+
  theme(plot.title = element_text(hjust = 0.5))
  
ggplotly(hhplot, tooltip = "text")
```

# Conscientiousness

Your score on conscientiousness shows that you are in the `r unique(hexaco_norm$cn_qscore)`th percentile for contientiousness. This means that you scored higher than `r unique(hexaco_norm$cn_qscore)`% of people on the dimension of contientiousness.

```{r con-plot, echo = F, warning = F}
cnplot <- ggplot(hexaco_norm, aes(x = cn))+
    geom_density(color = "orange4", fill = "orange1", linewidth = 0.9, bw = 0.3, alpha = 0.7)+
    geom_segment(aes(x = quantile(cn, probs = 0.5), y = 0, xend = quantile(cn, probs = 0.5), yend = 0.58, text = "Average"), color = "orange4", linetype = "dashed", linewidth = 0.4, alpha = 0.5)+
    geom_segment(aes(x = quantile(cn, probs = 0.01), y = 0.65, xend = quantile(cn, probs = 0.99), yend = 0.65), linewidth = 1, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.99), y = 0.65, text = "99th percentile"), size = 1.5, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.01), y = 0.65, text = "1st percentile"), size = 1.5, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.95), y = 0.65, text = "95th percentile"), size = 2, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.05), y = 0.65, text = "5th percentile"), size = 2, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.80), y = 0.65, text = "80th percentile"), size = 2.5, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.20), y = 0.65, text = "20th percentile"), size = 2.5, color = "orange3")+
    geom_point(aes(x = quantile(cn, probs = 0.5), y = 0.65, text = "Average"), size = 4, color = "orange3")+
    geom_segment(aes(x = cn_score, y = 0, xend = cn_score, yend = 0.65), color = "black", linewidth = 1)+
    geom_point(aes(x = cn_score, y = 0.65, text = cn_qscore), color = "black", size = 4.5)+
    geom_text(aes(x = cn_score, y = 0.68, label = "Your Score"))+
    theme_void()+
    scale_y_continuous(
      limits = c(0, 0.75),
      expand = c(0, 0))+
    labs(title = "Conscientiousness")+
  theme(plot.title = element_text(hjust = 0.5))
  
  
ggplotly(cnplot, tooltip = "text")
```

# Emotionality

Your score on emotionality shows that you are in the `r unique(hexaco_norm$em_qscore)`th percentile for emotionality. This means that you scored higher than `r unique(hexaco_norm$em_qscore)`% of people on the dimension of emotionality.

```{r emo-plot, echo = F, warning = F}
emplot <- ggplot(hexaco_norm, aes(x = em))+
    geom_density(color = "firebrick4", fill = "firebrick1", linewidth = 0.9, bw = 0.3, alpha = 0.7)+
    geom_segment(aes(x = quantile(em, probs = 0.5), y = 0, xend = quantile(em, probs = 0.5), yend = 0.53, text = "Average"), color = "firebrick", linetype = "dashed", linewidth = 0.4, alpha = 0.5)+
    geom_segment(aes(x = quantile(em, probs = 0.01), y = 0.6, xend = quantile(em, probs = 0.99), yend = 0.6), linewidth = 1, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.99), y = 0.6, text = "99th percentile"), size = 1.5, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.01), y = 0.6, text = "1st percentile"), size = 1.5, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.95), y = 0.6, text = "95th percentile"), size = 2, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.05), y = 0.6, text = "5th percentile"), size = 2, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.80), y = 0.6, text = "80th percentile"), size = 2.5, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.20), y = 0.6, text = "20th percentile"), size = 2.5, color = "firebrick")+
    geom_point(aes(x = quantile(em, probs = 0.5), y = 0.6, text = "Average"), size = 4, color = "firebrick")+
    geom_segment(aes(x = em_score, y = 0, xend = em_score, yend = 0.6), color = "black", linewidth = 1)+
    geom_point(aes(x = em_score, y = 0.6, text = em_qscore), color = "black", size = 4.5)+
    geom_text(aes(x = em_score, y = 0.63, label = "Your Score"))+
    theme_void()+
    scale_y_continuous(
      limits = c(0, 0.7),
      expand = c(0, 0))+
    labs(title = "Emotionality")+
  theme(plot.title = element_text(hjust = 0.5))
  
ggplotly(emplot, tooltip = "text")
```

# Openness to Experience

Your score on openness to experience shows that you are in the `r unique(hexaco_norm$op_qscore)`th percentile for openness to experience. This means that you scored higher than `r unique(hexaco_norm$op_qscore)`% of people on the dimension of openness to experience.

```{r open-plot, echo = F, warning = F}
opplot <- ggplot(hexaco_norm, aes(x = op))+
    geom_density(color = "purple4", fill = "purple1", linewidth = 0.9, bw = 0.3, alpha = 0.7)+
    geom_segment(aes(x = quantile(op, probs = 0.5), y = 0, xend = quantile(op, probs = 0.5), yend = 0.55, text = "Average"), color = "purple4", linetype = "dashed", linewidth = 0.4, alpha = 0.5)+
    geom_segment(aes(x = quantile(op, probs = 0.01), y = 0.6, xend = quantile(op, probs = 0.99), yend = 0.6), linewidth = 1, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.99), y = 0.6, text = "99th percentile"), size = 1.5, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.01), y = 0.6, text = "1st percentile"), size = 1.5, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.95), y = 0.6, text = "95th percentile"), size = 2, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.05), y = 0.6, text = "5th percentile"), size = 2, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.80), y = 0.6, text = "80th percentile"), size = 2.5, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.20), y = 0.6, text = "20th percentile"), size = 2.5, color = "purple3")+
    geom_point(aes(x = quantile(op, probs = 0.5), y = 0.6, text = "Average"), size = 4, color = "purple3")+
    geom_segment(aes(x = op_score, y = 0, xend = op_score, yend = 0.6), color = "black", linewidth = 1)+
    geom_point(aes(x = op_score, y = 0.6, text = op_qscore), color = "black", size = 4.5)+
    geom_text(aes(x = op_score, y = 0.63, label = "Your Score"))+
    theme_void()+
    scale_y_continuous(
      limits = c(0, 0.7),
      expand = c(0, 0))+
    labs(title = "Openness to Experience")+
  theme(plot.title = element_text(hjust = 0.5))
  
ggplotly(opplot, tooltip = "text")
```
